Introduction to *cellcount* - Draft vignette

### 2024-04-11 cellcount_intro.Rmd
Moved vingette file back to main folder
Minor updates to vignette files

```{r,message=FALSE}
savdir <- ("C:/file path for saving CSV data")
image_savdir <- ("C:/file path for saving converted images")
```
```{r,include=FALSE}
savdir <- ("./cellcount_files_HABF/inst/extdata/test_data/")
image_savdir <- ("./cellcount_files_HABF/inst/extdata/test_results/")
```

@@

```{r}
images <- list.files("./cellcount_files_HABF/inst/extdata/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = T)
images_names <- list.files("./cellcount_files_HABF/inst/extdata/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = F)
```

@@

savdir <- ("./cellcount_files_HABF/inst/extdata/test_data/")
image_savdir <- ("./cellcount_files_HABF/inst/extdata/test_results/")
images <- list.files("./cellcount_files_HABF/inst/extdata/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = T)
images_names <- list.files("./cellcount_files_HABF/inst/extdata/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = F)

@@

savdir <- ("./cellcount_files_HABF/inst/extdata/test_data/")
image_savdir <- ("./cellcount_files_HABF/inst/extdata/test_results/")
images <- list.files("./cellcount_files_HABF/inst/extdata/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = T)
images_names <- list.files("./cellcount_files_HABF/inst/extdata/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = F)

@@

![Visual demonstration of the Shiny GUI for inputting data.](C:/Users/Tyler.Harman/Pictures/cellcount-UI_1.png)

@@

![Visual demonstration of the Shiny GUI for running image analysis.](C:/Users/Tyler.Harman/Pictures/cellcount-UI_2.png)

>>>>

```{r,message=FALSE}
savdir <- ("C:/file path for saving CSV data")
image_savdir <- ("C:/file path for saving converted images")
```
```{r,include=FALSE}
savdir <- ("./inst/extdata/test_data/")
image_savdir <- ("./inst/extdata/test_results/")
```

@@

```{r}
images <- list.files("./inst/extdata/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = T)
images_names <- list.files("./inst/extdata/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = F)
```

@@

savdir <- ("./inst/extdata/test_data/")
image_savdir <- ("./inst/extdata/test_results/")
images <- list.files("./inst/extdata/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = T)
images_names <- list.files("./inst/extdata/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = F)

@@

savdir <- ("./inst/extdata/test_data/")
image_savdir <- ("./inst/extdata/test_results/")
images <- list.files("./inst/extdata/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = T)
images_names <- list.files("./inst/extdata/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = F)

@@

![Visual demonstration of the Shiny GUI for inputting data.](./inst/figures/cellcount-UI_1.png)

@@

![Visual demonstration of the Shiny GUI for running image analysis.](./inst/figures/cellcount-UI_2.png)
